Comprehensive Quality Awareness Automated Semantic Web Service Composition

### 2017-03-23 paper.tex
update

QoS-aware web service composition is studied using traditional approaches or Evolutionary Computation (EC) techniques. Qi et al. \cite{qi2010combining} propose a heuristic service composition method, where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near-to-optimal QoS. but there exists a scalability problem for the enumeration technique. EC techniques are used to automatically generate solutions with optimal QoS, which is considered to a NP-hard problem. Gupta et al. \cite{gupta2015optimization} employ an Genetic Algorithm using a set of binary strings as individuals, which demands to be decoded into composition solutions. Genetic Programming (GP) are used by \cite{yu2013adaptive} to find optimal solutions, which is reached by penalising infeasible solutions using a fitness function. A hybird approach employs both greedy search algorithm and GP is introduced in \cite{ma2015hybrid} to generate solutions with functional correctness. In particularly, a greedy search is used to generate  directed acyclic graphs (DAGs) as composition solutions that is further transferred to tree structures for initialisation and mutation. To eliminating the transformation process from DAGs, A promising GraphEvol is proposed in \cite{da2015graphevol}, where web service composition are in a form of DAGs employing Graph-based evolutionary operators like crossover and mutation. An indirect PSO-based approach was introduced in \cite{da2016particle}. An optimised queue is used as an indirect representation that is decoded into a DAG-based solution. These QoS-aware approaches \cite{gupta2015optimization,qi2010combining,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive} do not consider semantic matchmaking quality, which could lead to too specific outputs produced by the selected services, The finding is supported by our first comparison experiment.

@@

\begin{figure}[h]
\centering
\fbox{\includegraphics[scale=.25]{motivation.pdf}}
 \caption{ An example of a web service composition}
 \label{motivation}
\end{figure}

@@

\textbf{Semantic Web Service Model}. The semantic web service model represents web services with functional descriptions, and how interoperability of web services enables matchmaking for automatically generating composition solutions.

@@

\textbf{Composition Problem}
A set of semantic web services $S$ are chained as a weighted DAG composition mode $WG$ when a composition task $Comp.T$ is requested by users. The composition problem considered in this paper to automatically generate $WG$, satisfying the follows:

@@

\section{PSO-based Approach to Comprehensive Quality-Aware Automated Semantic Web Service Composition}\label{qswsc_approach}

@@

\section{Results and Analysis}\label{results_analysis}
\subsection{Comparison Test for Comprehensive Quality Evaluation Mode and QoS Evaluation Model}\label{comparisonTest}
To analyse the differences between optimal solutions evaluated by comprehensive evaluation model and QoS evluation mode, We first look at the $MT$, $S$ and $QoS$

QoS-aware web service composition \cite{da2016particle,da2015graphevol,yu2013adaptive,ma2015hybrid} do consider two semantic matchmaking types (Exact and Plugin) for discovering desired web service, but there is no measurement of matchmaking types and concept similarity, so the weights for $MT$ and $S$ are considered to be 0. Consequently, our evaluation mode become a widely used fitness function \cite{ma2015hybrid,da2016particle}, $Fitness = w_1 \hat{A} + w_2 \hat{R} + w_3(1 - \hat{T}) + w_4(1 - \hat{C})$ when $\sum_{i=1}^{4} w_i = 1$  for QoS-aware web service composition. To compare the composition solution generated by our approach with QoS-aware approach. We look at mean value of $MT$, $S$ and $QoS$ at optimum at the 100th generation for two approaches. In QoS-aware approach, $MT$ and $S$ are recorded, and $QoS$ is normalised from 0 to 0.5 to make it comparable, besides that, all weights in QoS-aware fitness function are set equally to 0.25.

We observe an interesting pattern from Table \ref{decisionTable} using statistic analysis: mean value of $MT$ and $S$ at optimum by our approach is consistently higher than those by QoS-aware approach.  Meanwhile, $QoS$ generated by QoS-aware approach can achieve a more desirable tradeoff in both semantic matchmaking quality and QoS.

\begin{table}[]
\footnotesize
\centering
\caption{Mean Quality for comprehensive quality-aware methods and QoS-aware approach}
\label{decisionTable}
\begin{tabular}{l|l|l|l}
\hline
\multicolumn{2}{c|}{WSC09}              & \shortstack{QoS-aware \\ Evaluation} & \shortstack{Comprehensive \\ Quality Evaluation} \\ \hline
\multirow{3}{*}{Task1}  &$MT$   &0.189787 $\pm$ 0.039278686            &0.221862 $\pm$ 0.009582 $\uparrow$ \\ \cline{2-4} 
                        &$S$    &0.884962 $\pm$ 0.014140               &0.894082 $\pm$ 0.009206 $\uparrow$ \\ \cline{2-4}
                        &$QoS$  &0.278730 $\pm$ 0.007786               &0.280222 $\pm$ 0.008212                          \\ \hline
\multirow{3}{*}{Task2}  &$MT$   &0.001795 $\pm$ 0.000719               &0.001977 $\pm$ 0.001566 $\uparrow$ \\ \cline{2-4} 
                        &$S$    &0.906971 $\pm$ 0.005855               &0.923970 $\pm$ 0.006898 $\uparrow$   \\ \cline{2-4}
                        &$QoS$  &0.239979 $\pm$ 0.000578 $\uparrow$    &0.238596 $\pm$ 0.001264 \\ \hline
\multirow{3}{*}{Task3}  &$MT$   &0.158526 $\pm$ 0.014028               &0.245830 $\pm$ 0.007761 $\uparrow$   \\ \cline{2-4} 
                        &$S$    &0.949109 $\pm$ 0.002331               &0.972765 $\pm$ 0.002980 $\uparrow$           \\ \cline{2-4}
                        &$QoS$  &0.247002 $\pm$ 0.000661 $\uparrow$    &0.245631 $\pm$ 0.000431            \\ \hline
\multirow{3}{*}{Task4}  &$MT$   &0.000000 $\pm$ 0.000000               &0.000004 $\pm$ 0.000002 $\uparrow$ \\ \cline{2-4} 
                        &$S$    &0.879514 $\pm$ 0.007456               &0.920733 $\pm$ 0.000001 $\uparrow$ \\ \cline{2-4}
                        &$QoS$  &0.242297 $\pm$ 0.000507 $\uparrow$    &0.236677 $\pm$ 0.002211  \\ \hline
\multirow{3}{*}{Task5}  &$MT$   &  0.000042 $\pm$ 0.000030             &0.000078 $\pm$ 0.000020 $\uparrow$           \\ \cline{2-4} 
                        &$S$    &  0.915933 $\pm$ 0.012888             &0.927678 $\pm$ 0.002578 $\uparrow$                 \\ \cline{2-4}
                        &$QoS$  & 0.238189 $\pm$ 0.000240 $\uparrow$      &  0.237485 $\pm$  0.000328  \\ \hline                                                   
\end{tabular}
\end{table}

To better understand that our evaluation approach could generate solutions having better semantic matchmaking quality with a slight trade-off in $QoS$, we demonstrate an example solution to Task 3. Fig. \ref{comparisontest} $(1)$ and $(2)$ are two weighted DAGs as best solutions found employing QoS-aware approach and Comprehensive quality-aware method respectively. Two approaches generate exactly the same service workflow structure while some service vertices and edges denoted in red are different. We list the semantic matchmaking quality represented by all edges ($e_1$ to $e4$), overall semantic matchmaking quality and QoS in Fig. \ref{comparisontest} $(3)$. To demonstrate how different the semantic matchmaking quality is, we analyse $e_4$ that has the smallest $\Delta Q$, which reveals the gain (positive $\Delta Q$) or loss (negative $\Delta Q$) for the listed qualities using our approach. The $e_4$ has two different source service vertices ($Ser1640238160$ and $Ser1947554374$) and the same $end$ vertices in two solutions. The outputs of two different source service are marked on the related taxonomy in Fig. \ref{comparisontest} $(4)$, $Ser1640238160$ and $Ser1947554374$ are service with output concept-related parameters $Inst795998200$ and $Inst582785907$ corresponding to two concepts $Con103314376$ and $Con2037585750$ respectively, and $Inst658772240$ are the required parameter for the $end$ vertice, which is related to concept $Con2113572083$. There exist $Inst795998200$ $\in$ $Con103314376$ $\sqsubseteq_{2}$ $Inst658772240$ $\in$ $Con2113572083$ and $Inst582785907$ $\in$ $Con2037585750$ $\sqsubseteq_{3}$ $Inst658772240$ $\in$ $Con2113572083$. It is obvious that our approach selects the service providing $Inst795998200$ that are closer to the users' required outputs.
\begin{figure}[h]
\centering{
\fbox{
\includegraphics[scale=.22]{comparisontest.pdf}}}
 \caption{Example Comparison of solutions to Task 3 using two different evaluation model.}
 \label{comparisontest}
\end{figure}

\subsection{Comparison Test with GP-based approach}\label{comparisonTestWithGP}
To evaluate the performance of our proposed PSO-based approach, we compare one GP-based approach  \cite{ma2015hybrid} with our PSO method. We consider the links between child nodes and parent nodes as semantic web service links for measuring  semantic matchmaking quality, and those links information are maintained correctly for the crossover and mutation. Therefore, we evaluate both semantic matchmaking quality and QoS simultaneously using the proposed comprehensive quality model. To make a fair comparison with our PSO-based, we consider the same number of evaluations (3000 times) as that in our PSO-based approach, we set the parameters settings for GP-based approach \cite{ma2015hybrid} using 30 individuals and 100 generations.

>>>>

QoS-aware web service composition is studied using traditional approaches or Evolutionary Computation (EC) techniques. Qi et al. \cite{qi2010combining} propose a heuristic service composition method, where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near-to-optimal QoS. but there exists a scalability problem for the enumeration technique. EC tecQoS-aware web service composition \cite{da2016particle,da2015graphevol,yu2013adaptive,ma2015hybrid}hniques are used to automatically generate solutions with optimal QoS, which is considered to a NP-hard problem. Gupta et al. \cite{gupta2015optimization} employ an Genetic Algorithm using a set of binary strings as individuals, which demands to be decoded into composition solutions. Genetic Programming (GP) are used by \cite{yu2013adaptive} to find optimal solutions, which is reached by penalising infeasible solutions using a fitness function. A hybird approach employs both greedy search algorithm and GP is introduced in \cite{ma2015hybrid} to generate solutions with functional correctness. In particularly, a greedy search is used to generate  directed acyclic graphs (DAGs) as composition solutions that is further transferred to tree structures for initialisation and mutation. To eliminating the transformation process from DAGs, A promising GraphEvol is proposed in \cite{da2015graphevol}, where web service composition are in a form of DAGs employing Graph-based evolutionary operators like crossover and mutation. An indirect PSO-based approach was introduced in \cite{da2016particle}. An optimised queue is used as an indirect representation that is decoded into a DAG-based solution. These QoS-aware approaches \cite{gupta2015optimization,qi2010combining,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive} do not consider semantic matchmaking quality, which could lead to too specific outputs produced by the selected services, The finding is supported by our first comparison experiment.

@@

\begin{figure}[h]
\centering
\fbox{\includegraphics[scale=.25]{motivation.pdf}}
 \caption{ An example of a web service composition}
 \label{motivation}
\end{figure}QoS-aware web service composition \cite{da2016particle,da2015graphevol,yu2013adaptive,ma2015hybrid}

@@

\textbf{Semantic Web Service Model}. The semantic web service model represents web services with functional descriptions, and how interoperability of web services enables matchmaking for automatically generating composition solutions.QoS-aware web service composition \cite{da2016particle,da2015graphevol,yu2013adaptive,ma2015hybrid}

@@

\textbf{Composition Problem}
A set of semantic web services $S$ are chained as a weighted DAG composition model $WG$ when a composition task $Comp.T$ is requested by users. The composition problem considered in this paper to automatically generate $WG$, satisfying the follows:

@@

Our comprehensive quality evaluation model is considered to be more general. Semantic matchmaking types (Exact and Plugin) are considered for discovering desired web service in QoS-aware web service composition  \cite{ma2015hybrid,da2016particle,da2015graphevol}, but there are no measurements of matchmaking types and concept similarities. Consequently, weights for $MT$ and $S$ are considered to be 0 in our propopsed comprehensive evaluation model, it turns to a widely used QoS evaluation model in \cite{ma2015hybrid,da2016particle,da2015graphevol}.
\section{PSO-based Approach to Comprehensive Quality-Aware Automated Semantic Web Service Composition}\label{qswsc_approach}

@@

\section{Results and Analysis}\label{results_analysis}
\subsection{Comparison Test for Comprehensive Quality Evaluation Model and QoS Evaluation Model}\label{comparisonTest}

A recent widely used QoS Evaluation Model, $QoS = w_1 \hat{A} + w_2 \hat{R} + w_3(1 - \hat{T}) + w_4(1 - \hat{C})$, where $\sum_{i=1}^{4} w_i = 1$, is used for QoS-aware web service composition \cite{ma2015hybrid,da2016particle,da2015graphevol}. We employ this QoS evluation model and our proposed comprehensive quality evluation model using our proposed PSO-based approach for searching for optimal solutions.
To analyse the differences in optimal solutions found by these two evaluation model, we recorded and compared the different mean values of $MT$, $S$, $QoS$ at the 100th generation over 30 runs. To make a sense of the comparison, all these recorded values are normalised from 0 to 1, and compared using statistical analysis in in Table \ref{decisionTable}.

We observe an interesting pattern from Table \ref{decisionTable}. The mean values of $QoS$ using QoS evaluation model are significantly higher than those using comprehensive quality evaluation model for Task 2, 3, 4 and 5,  but the mean value of $MT$ and $S$ using comprehensive quality evaluation model are consistently significantly higher than those using QoS evluation model for all tasks with a slight trade-off in $QoS$.

\begin{table}[]
\footnotesize
\centering
\caption{Mean values of $MT$, $S$, and $QoS$ for QoS Evaluation Model and Comprehensive Quality Evaluation Model using PSO-based approach}
\label{decisionTable}
\begin{tabular}{l|l|l|l}
\hline
\multicolumn{2}{c|}{WSC09}              & QoS Evaluation Model         &\shortstack{Comprehensive \\ Quality Evaluation Model} \\ \hline
\multirow{3}{*}{Task1}  &$MT$   &0.189787 $\pm$ 0.039278686            &0.221862 $\pm$ 0.009582 $\uparrow$ \\ \cline{2-4} 
                        &$S$    &0.884962 $\pm$ 0.014140               &0.894082 $\pm$ 0.009206 $\uparrow$ \\ \cline{2-4}
                        &$QoS$  &0.278730 $\pm$ 0.007786               &0.280222 $\pm$ 0.008212                          \\ \hline
\multirow{3}{*}{Task2}  &$MT$   &0.001795 $\pm$ 0.000719               &0.001977 $\pm$ 0.001566 $\uparrow$ \\ \cline{2-4} 
                        &$S$    &0.906971 $\pm$ 0.005855               &0.923970 $\pm$ 0.006898 $\uparrow$   \\ \cline{2-4}
                        &$QoS$  &0.239979 $\pm$ 0.000578 $\uparrow$    &0.238596 $\pm$ 0.001264 \\ \hline
\multirow{3}{*}{Task3}  &$MT$   &0.158526 $\pm$ 0.014028               &0.245830 $\pm$ 0.007761 $\uparrow$   \\ \cline{2-4} 
                        &$S$    &0.949109 $\pm$ 0.002331               &0.972765 $\pm$ 0.002980 $\uparrow$           \\ \cline{2-4}
                        &$QoS$  &0.247002 $\pm$ 0.000661 $\uparrow$    &0.245631 $\pm$ 0.000431            \\ \hline
\multirow{3}{*}{Task4}  &$MT$   &0.000000 $\pm$ 0.000000               &0.000004 $\pm$ 0.000002 $\uparrow$ \\ \cline{2-4} 
                        &$S$    &0.879514 $\pm$ 0.007456               &0.920733 $\pm$ 0.000001 $\uparrow$ \\ \cline{2-4}
                        &$QoS$  &0.242297 $\pm$ 0.000507 $\uparrow$    &0.236677 $\pm$ 0.002211  \\ \hline
\multirow{3}{*}{Task5}  &$MT$   &  0.000042 $\pm$ 0.000030             &0.000078 $\pm$ 0.000020 $\uparrow$           \\ \cline{2-4} 
                        &$S$    &  0.915933 $\pm$ 0.012888             &0.927678 $\pm$ 0.002578 $\uparrow$                 \\ \cline{2-4}
                        &$QoS$  & 0.238189 $\pm$ 0.000240 $\uparrow$      &  0.237485 $\pm$  0.000328  \\ \hline                                                   
\end{tabular}
\end{table}

To better understand a better semantic matchmaking quality with a slight trade-off in the opitmal solutions using comprehensive quality evaluation model, we demonstrate the optimal solutions using task 3 as an example. Fig. \ref{comparisontest} $(1)$ and $(2)$ show two weighted DAGs as best solutions found by employing QoS-aware approach and Comprehensive quality-aware method respectively. Two approaches generate exactly the same service workflow structure, but some service vertices and edges denoted in red are different. To better understand these differences, we list the overall semantic matchmaking quality $SM$,  overall $QoS$ and semantic matchmaking quality associated to each edge ($sm_{e_1}$ to $sm_{e_4}$) for the two weighted DAGs in Fig. \ref{comparisontest} $(3)$, where $\Delta Q$ reveals the gain (positive $\Delta Q$) or loss (negative $\Delta Q$) for the listed qualities using our comprehensive quality evalutaion model. Therefore, an overall gain 0.1433 is calculated from a sum of $SM$ gain (0.1467) and $QoS$ loss (-0.0034). Consequently, our comprehensive evaluation model acheive a desirable trade-off in considering both semantic matchmaking and QoS. To demonstrate the value of semantic matchmking gain, we pick up $e_4$ associated with a smallest $\Delta Q$, where edeges $e_4$ to $WG(1)$ using QoS evaluation model and $WG(2)$ using comprehensive quality model have two different source service vertices $Ser1640238160$ and $Ser1947554374$ respectively,  and the same $end$ vertices. $Ser1640238160$ and $Ser1947554374$ are services with concept-related output parameters $Inst795998200$ and $Inst582785907$ corresponds to two concepts $Con103314376$ and $Con2037585750$ respectively marked on the related taxonomy in Fig. \ref{comparisontest} $(4)$. These two services $Ser1640238160$ and $Ser1947554374$ are associated with concept-related output parameters $Inst795998200$ and $Inst582785907$, and these parameters  are corresponds to two concepts $Con103314376$ and $Con2037585750$ respectively marked on the related taxonomy in Fig. \ref{comparisontest} $(4)$. In addtion, $Inst658772240$ are the required parameter for the $end$ vertice, which is related to concept $Con2113572083$. There exist $Inst582785907$ $\in$ $Con2037585750$ $\sqsubseteq_{3}$ $Inst658772240$ $\in$ $Con2113572083$ for $e_4$ in $WG(1)$ and $Inst795998200$ $\in$ $Con103314376$ $\sqsubseteq_{2}$ $Inst658772240$ $\in$ $Con2113572083$ for $e_4$ in $WG(2)$. Therefore, 2-levels Subsumes is closer 3-level Subsumes, $Inst795998200$ is closer to user's required outputs $Inst658772240$ compared with $Inst582785907$.

\begin{figure}[h]
\centering{
\fbox{
\includegraphics[scale=.22]{comparisontest.pdf}}}
 \caption{Example Comparison of solutions to Task 3 using two different evaluation model.}
 \label{comparisontest}
\end{figure}

\subsection{Comparison Test with GP-based approach}\label{comparisonTestWithGP}
To evaluate the performance of our proposed PSO-based approach, we compare one GP-based approach  \cite{ma2015hybrid} with our PSO method. we consider the links between child nodes and parent nodes as semantic web service links for measuring  semantic matchmaking quality, and those links information are maintained correctly for the crossover and mutation. Therefore, we evaluate both semantic matchmaking quality and QoS simultaneously using the proposed comprehensive quality model. To make a fair comparison with our PSO-based, we consider the same number of evaluations (3000 times) as that in our PSO-based approach, we set the parameters settings for GP-based approach \cite{ma2015hybrid} using 30 individuals and 100 generations.
